Are rankings of financial analysts useful to investors?

### 2015-03-19 doc/paper/paper-knitr-APS.Rnw
add APS comment on having the recent TPER for all rankings (true,naive,default)

test <- melt(stat.full,id.vars = c('year','Method','Strategy','type'))
test.a <- acast(test,year~Method~Strategy~variable~type,value.var = 'value')

@@

@@

periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat','type')),period~Views~Method~strat~variable~type,value.var = 'value')

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
&all&same&all&same&all&same\\
\midrule
<<desc-q-cons,echo=F,results='asis'>>=
test.a[,,,1:2,] <- test.a[,,,1:2,]*100
dimnames(test.a)[[2]] <- c('\\tr{}','\\naive{}','\\default{}')
print(xtable(acast(melt(test.a[12,,'CONS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

@@

%\resizebox{\textwidth}{!}{%
%\begin{tabular}{rrrrrrr}
\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
&all&same&all&same&all&same\\
<<stocks-true,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[,1,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

@@

<<bl-nr,echo=F,results='asis'>>=
print(xtable(acast(melt(bl.results[1:3,1,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabular}}

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))

>>>>

test <- melt(stat.full,id.vars = c('year','Method','Strategy','type'))
test.a <- acast(test,year~Method~Strategy~variable~type,value.var = 'value')
test.a[,'true','CONS',,] <- NA

@@

bl.results['CONS','true',,] <- NA

@@

periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat','type')),period~Views~Method~strat~variable~type,value.var = 'value')
periods.array[,'CONS','true',,,] <- NA

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
&all&same&all&same&all&same\\
\midrule
<<desc-q-cons,echo=F,results='asis'>>=
test.a[,,,1:2,] <- test.a[,,,1:2,]*100
dimnames(test.a)[[2]] <- c('\\tr{}','\\naive{}','\\default{}')
print(xtable(acast(melt(test.a[12,1:3,'CONS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

@@

%\resizebox{\textwidth}{!}{%
%\begin{tabular}{rrrrrrr}
\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
&all&same&all&same&all&same\\
<<stocks-true,echo=F,results='asis'>>=
print(xtable(acast(melt(test.a[,1,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

@@

<<bl-nr,echo=F,results='asis'>>=
print(xtable(acast(melt(bl.results[1:3,1,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,NA.string='-',include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabular}}

@@

print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,NA.string='-',include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))

### 2015-03-19 doc/paper/paper-knitr-APS.tex
add APS comment on having the recent TPER for all rankings (true,naive,default)

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.577\%, 18.615\%, and 21.218\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (15.719\%, 15.738\%, and 18.836\%). Panel C shows the EPS based weighted expected returns averages (14.893\%, 14.895\%, and 19.394\%).

@@

\subsection{Perfect foresight strategy}
\label{sec:perfect}
Panel B presents the results for the case of the \tr{} information set. The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, 1.893\%, 5.116\%, 1.86\%. All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%). The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be. In any case, the results suggest that the advice of analysts, as a group, is valuable. 
%Yet, the top analyst

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio is 0.351 against 0.125, 0.123, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period as expected.

@@

Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\ensuremath{-0.005}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\ensuremath{-0.032}\% and 0.441\% respectively). The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
&all&same&all&same&all&same\\
\midrule
  \multicolumn{7}{c}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & 18.577 & 18.947 & 16.861 & 17.156 & 0.119 & 0.119 \\ 
  \naive{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\ 
  \default{} & 21.218 & 21.729 & 19.742 & 20.014 & 0.107 & 0.106 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \midrule
  \multicolumn{7}{c}{\textbf{Panel B: TP}} \\ 
 \midrule 
\tr{} & 15.719 & 16.071 & 14.303 & 14.525 & 0.098 & 0.098 \\ 
  \naive{} & 15.738 & 16.098 & 14.304 & 14.528 & 0.098 & 0.098 \\ 
  \default{} & 18.836 & 19.352 & 17.795 & 18.195 & 0.086 & 0.084 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \multicolumn{7}{c}{\textbf{Panel C: EPS}} \\ 
 \midrule 
\tr{} & 14.893 & 14.964 & 13.407 & 13.449 & 0.102 & 0.103 \\ 
  \naive{} & 14.895 & 14.967 & 13.393 & 13.432 & 0.103 & 0.103 \\ 
  \default{} & 19.394 & 19.511 & 18.602 & 18.756 & 0.088 & 0.089 \\

@@

%\resizebox{\textwidth}{!}{%
%\begin{tabular}{rrrrrrr}
\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
&all&same&all&same&all&same\\
  \multicolumn{7}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 &  219 &  202 &  219 &  202 &  144 &  145 \\ 
  2000 &  295 &  269 &  295 &  269 &  211 &  211 \\ 
  2001 &  341 &  306 &  341 &  306 &  257 &  257 \\ 
  2002 &  374 &  333 &  374 &  333 &  299 &  299 \\ 
  2003 &  390 &  346 &  390 &  346 &  311 &  311 \\ 
  2004 &  399 &  351 &  399 &  351 &  331 &  331 \\ 
  2005 &  414 &  358 &  414 &  358 &  343 &  343 \\ 
  2006 &  421 &  360 &  421 &  360 &  344 &  344 \\ 
  2007 &  426 &  364 &  426 &  364 &  357 &  357 \\ 
  2008 &  420 &  360 &  420 &  360 &  339 &  339 \\ 
  2009 &  365 &  323 &  365 &  323 &  300 &  300 \\ 
   \midrule 
Total &  442 &  378 &  442 &  378 &  376 &  376 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \multicolumn{7}{l}{\textbf{Panel C: \default{}}} \\ 
 \midrule 
1999 &   73 &   69 &   73 &   69 &   54 &   54 \\ 
  2000 &  257 &  235 &  257 &  235 &  205 &  205 \\ 
  2001 &  314 &  284 &  314 &  284 &  264 &  264 \\ 
  2002 &  368 &  327 &  368 &  327 &  308 &  308 \\ 
  2003 &  383 &  341 &  383 &  341 &  326 &  326 \\ 
  2004 &  396 &  350 &  396 &  350 &  339 &  339 \\ 
  2005 &  414 &  364 &  414 &  364 &  357 &  357 \\ 
  2006 &  429 &  370 &  429 &  370 &  365 &  365 \\ 
  2007 &  438 &  374 &  438 &  374 &  371 &  371 \\ 
  2008 &  440 &  376 &  440 &  376 &  375 &  375 \\ 
  2009 &  442 &  378 &  442 &  378 &  378 &  378 \\ 
   \midrule 
Total &  442 &  378 &  442 &  378 &  378 &  378 \\

@@

 \textit{CONS} & 1.893 & 2.247 & 15.147 & 15.032 & 0.125 & 0.149 &  291 &  257 & 0.291 & 0.277 \\ 
  \textit{TP} & 5.116 & 5.400 & 14.593 & 14.552 & 0.351 & 0.371 &  291 &  257 & 0.314 & 0.298 \\ 
  \textit{EPS} & 1.860 & 1.957 & 15.172 & 15.145 & 0.123 & 0.129 &  209 &  209 & 0.503 & 0.501 \\ 
   \midrule

@@

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & -0.032 & 0.478 & 15.827 & 15.860 & -0.002 & 0.030 &  290 &  257 & 0.189 & 0.187 \\ 
  \textit{TP} & -0.005 & 0.441 & 15.633 & 15.658 & -0.000 & 0.028 &  290 &  257 & 0.192 & 0.189 \\ 
  \textit{EPS} & 0.441 & 0.441 & 15.673 & 15.702 & 0.028 & 0.028 &  250 &  250 & 0.198 & 0.198 \\

@@

  \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 4.476 & 0.287 & 6.780 & 0.447 & 3.577 & 0.232 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 3.948 & 0.261 & 6.937 & 0.477 & 4.558 & 0.311 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 6.201 & 0.485 & 9.785 & 0.794 & 6.455 & 0.540 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 10.432 & 1.201 & 14.850 & 1.844 & 10.713 & 1.299 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -2.931 & -0.233 & 1.676 & 0.136 & -2.132 & -0.173 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -0.627 & -0.042 & 3.477 & 0.242 & 0.171 & 0.011 \\ 
   \midrule 
All period & -3.032 & -0.182 & 1.893 & 0.125 & 5.116 & 0.351 & 1.860 & 0.123 \\

@@

\midrule
\end{tabular}}
\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 3.891 & 0.251 & 3.537 & 0.233 & 4.177 & 0.276 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 3.581 & 0.234 & 3.738 & 0.252 & 4.232 & 0.283 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.604 & 0.431 & 5.863 & 0.469 & 5.969 & 0.490 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 8.217 & 0.865 & 8.554 & 0.962 & 8.572 & 0.970 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -5.999 & -0.435 & -5.690 & -0.415 & -5.561 & -0.403 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -3.806 & -0.233 & -3.427 & -0.210 & -3.161 & -0.193 \\ 
   \midrule 
All period & -3.032 & -0.182 & -0.032 & -0.002 & -0.005 & -0.000 & 0.441 & 0.028 \\

>>>>

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, NA\%, 18.615\%, and 18.615\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (14.876\%, 15.738\%, and 12.461\%). Panel C shows the EPS based weighted expected returns averages (14.696\%, 14.895\%, and 12.857\%).

@@

\subsection{Perfect foresight strategy}
\label{sec:perfect}
Panel B presents the results for the case of the \tr{} information set. The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, NA\%, 4.288\%, 0.565\%. All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%). The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be. In any case, the results suggest that the advice of analysts, as a group, is valuable. 
%Yet, the top analyst

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio is 0.292 against NA, 0.036, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period as expected.

@@

Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (0.681\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.323\% and 0.738\% respectively). The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
&all&same&all&same&all&same\\
\midrule
  \multicolumn{7}{c}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & - & - & - & - & - & - \\ 
  \naive{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\ 
  \default{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \midrule
  \multicolumn{7}{c}{\textbf{Panel B: TP}} \\ 
 \midrule 
\tr{} & 14.876 & 15.191 & 13.369 & 13.595 & 0.096 & 0.096 \\ 
  \naive{} & 15.738 & 16.098 & 14.304 & 14.528 & 0.098 & 0.098 \\ 
  \default{} & 12.461 & 12.718 & 10.588 & 10.789 & 0.088 & 0.089 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \multicolumn{7}{c}{\textbf{Panel C: EPS}} \\ 
 \midrule 
\tr{} & 14.696 & 14.774 & 13.233 & 13.269 & 0.101 & 0.102 \\ 
  \naive{} & 14.895 & 14.967 & 13.393 & 13.432 & 0.103 & 0.103 \\ 
  \default{} & 12.857 & 12.928 & 11.410 & 11.440 & 0.089 & 0.089 \\

@@

%\resizebox{\textwidth}{!}{%
%\begin{tabular}{rrrrrrr}
\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
&all&same&all&same&all&same\\
  \multicolumn{7}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 & - & - &   73 &   69 &   44 &   44 \\ 
  2000 & - & - &  253 &  232 &  191 &  191 \\ 
  2001 & - & - &  302 &  273 &  244 &  244 \\ 
  2002 & - & - &  354 &  317 &  290 &  290 \\ 
  2003 & - & - &  369 &  330 &  299 &  299 \\ 
  2004 & - & - &  375 &  331 &  318 &  318 \\ 
  2005 & - & - &  395 &  347 &  337 &  337 \\ 
  2006 & - & - &  403 &  351 &  337 &  337 \\ 
  2007 & - & - &  418 &  359 &  351 &  351 \\ 
  2008 & - & - &  414 &  354 &  339 &  339 \\ 
  2009 & - & - &  346 &  306 &  306 &  306 \\ 
   \midrule 
Total & - & - &  442 &  378 &  375 &  375 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \multicolumn{7}{l}{\textbf{Panel C: \default{}}} \\ 
 \midrule 
1999 &   73 &   69 &   73 &   69 &   54 &   54 \\ 
  2000 &  257 &  235 &  257 &  235 &  204 &  204 \\ 
  2001 &  310 &  281 &  310 &  281 &  261 &  261 \\ 
  2002 &  362 &  323 &  362 &  323 &  304 &  304 \\ 
  2003 &  374 &  334 &  374 &  334 &  317 &  317 \\ 
  2004 &  385 &  341 &  385 &  341 &  332 &  332 \\ 
  2005 &  401 &  352 &  401 &  352 &  344 &  344 \\ 
  2006 &  415 &  358 &  415 &  358 &  353 &  353 \\ 
  2007 &  421 &  361 &  421 &  361 &  358 &  358 \\ 
  2008 &  422 &  360 &  422 &  360 &  359 &  359 \\ 
  2009 &  405 &  351 &  405 &  351 &  350 &  350 \\ 
   \midrule 
Total &  442 &  378 &  442 &  378 &  377 &  377 \\

@@

 \textit{CONS} & - & - & - & - & - & - & - & - & - & - \\ 
  \textit{TP} & 4.288 & 4.512 & 14.695 & 14.792 & 0.292 & 0.305 &  284 &  251 & 0.344 & 0.326 \\ 
  \textit{EPS} & 0.565 & 0.718 & 15.541 & 15.509 & 0.036 & 0.046 &  205 &  205 & 0.495 & 0.493 \\ 
   \midrule

@@

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & 0.323 & 0.702 & 15.771 & 15.820 & 0.020 & 0.044 &  284 &  252 & 0.228 & 0.223 \\ 
  \textit{TP} & 0.681 & 1.043 & 15.553 & 15.476 & 0.044 & 0.067 &  284 &  252 & 0.256 & 0.248 \\ 
  \textit{EPS} & 0.738 & 0.711 & 15.446 & 15.481 & 0.048 & 0.046 &  245 &  245 & 0.256 & 0.255 \\

@@

  \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & - & - & 5.783 & 0.391 & 1.855 & 0.121 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & - & - & 6.081 & 0.422 & 3.861 & 0.263 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & - & - & 9.116 & 0.757 & 5.872 & 0.490 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & - & - & 14.705 & 1.913 & 10.700 & 1.367 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & - & - & 0.905 & 0.069 & -3.106 & -0.231 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & - & - & 2.814 & 0.188 & -0.709 & -0.044 \\ 
   \midrule 
All period & -3.032 & -0.182 & - & - & 4.288 & 0.292 & 0.565 & 0.036 \\

@@

\midrule
\end{tabular}}
\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 3.128 & 0.199 & 3.127 & 0.204 & 3.501 & 0.232 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 3.040 & 0.196 & 3.725 & 0.249 & 3.917 & 0.261 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.417 & 0.418 & 5.794 & 0.464 & 5.711 & 0.468 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 9.410 & 1.069 & 10.329 & 1.244 & 9.981 & 1.198 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -4.873 & -0.359 & -3.945 & -0.289 & -4.237 & -0.310 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -2.405 & -0.149 & -1.708 & -0.106 & -1.951 & -0.122 \\ 
   \midrule 
All period & -3.032 & -0.182 & 0.323 & 0.020 & 0.681 & 0.044 & 0.738 & 0.048 \\
